---
title: "Indroduction to binomial packages"
author: "Yuxin Zhang"
date: "2019年5月1日"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(binomial)
```

## binomial

The package `"binomial"` is a implementation for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.


## Function bin_choose()

A main function bin_choose() that calculates the number of
combinations in which k successes can occur in n trials.

```{r}
bin_choose(n = 5, k = 2)
```


## Function bin_probability()


This function find the probability of getting the number of successs in trials with a probability of success on each trial, and take take three arguments: success, trials, and prob.

```{r}
# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)
```


## Creating a `bindis`

The primary class is "bindis" indicating that this is an object of class binomial distribution. Additionally, to keep this object as a data frame.This function should return a data frame with the probability distribution: sucesses in the first column, probability in the second column.

```{r}
# binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)
```

use the function `plot()` to graph a barplot to display the probability histogram of a binomial distribution object `bindis`.

```{r}
# plotting binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

## Creating a `bincum`


The primary class is "bincum" indicating that this is an object of class binomial cumulative distribution. Additionally, to keep this object as a data frame.This function should return a data frame with both the probability distribution and the cumulative probabilities: sucesses in the first column, probability in the second column, and cumulative in the third column.

```{r}
# binomial cumulative distribution
bin_cumulative(trials = 5, prob = 0.5)
```

Once you have defined a `"coin"` object, you can use the function `plot()` to graph the cumulative distribution in object `bincum`.

```{r}
# plotting binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

## Creating a 'binvar'

This is a binomial random variable object.The returned object should be a list with named elements:
– trials: number of trials
– prob: probability of success
And it will nicely print the content of an object `binvar`.


```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
```


To get a full summary description of an object `binvar`

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

## Functions of measures

The mean of a binominal distribution

```{r}
bin_mean(10, 0.3)
```

The variance of a binominal distribution

```{r}
bin_variance(10, 0.3)
```

The mode of a binominal distribution

```{r}
bin_mode(10, 0.3)
```

The skewness of a binominal distribution

```{r}
bin_skewness(10, 0.3)
```

The kurtosis of a binominal distribution

```{r}
bin_kurtosis(10, 0.3)
```
